An Extension of Two-Dimensional Detection Function Distance Sampling Software

### 2018-02-04 Draft.tex
strip sampling

\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{StripSampling}
\caption{Example distribution of animals in a square survey area divided into 5 equal strips}

\end{figure}

\subsubsection{The significance of 2D detection functions}
\subsection{Previous contributions}

>>>>

\begin{figure}[H]
\centering
\includegraphics[scale=0.5]{StripSampling}
\caption{Example distribution of animals in a square survey area divided into 5 equal strips}
\end{figure}

Given this rather simplistic design, obtaining an estimate of abundance in the survey area ($\hat{n}$) is extremely simple, so long as we are able to sample all of the individuals within whole strips. As an example we consider strips 2 and 3 (from the left) as randomly selected strips which form our sample. Strip 2 contains

\subsubsection{The significance of 2D detection functions}

test
\subsection{Previous contributions}
